Scagnostics and Projection Pursuit

### 2018-01-31 Draft/Draft.Rmd
Adding mbgraphic examples.

>>>>

Additions to the standard scagnostics measures have been implemented in the package mbgraphics, based on splines (spline2d) and distance correlation (dcor2d).
Give definitions here..
We repeat the study from before, we first test in Figure ADDREF the behaviour of the index values over 100 interpolated projections that are randomly selected via the grand tour algorithm.
Note that here the measures are calculated on non-binned data.
The observed behaviour is smooth (much in contrast to the behaviour of the scagnostics measures) and we next test the behaviour in a guided tour, comparing again also the first and final projection. (which index to select, will try both below...)
```{r mbgraphics-indices, fig.height=3, fig.cap="(ref:mbgraphics-indices)"}
```
```{r guided-spline2d, include=FALSE}
```
```{r guided-spline2d-plot, fig.height=3, fig.cap="(ref:guided-spline2d-plot)"}
```
maybe move timing to the end, add also these indices in the same plot (instead of testing several samples, behaviour anyway similar)

### 2018-01-31 Draft/Draft.tex
Adding mbgraphic examples.

>>>>

Additions to the standard scagnostics measures have been implemented in
the package mbgraphics, based on splines (spline2d) and distance
correlation (dcor2d). Give definitions here.. We repeat the study from
before, we first test in Figure ADDREF the behaviour of the index values
over 100 interpolated projections that are randomly selected via the
grand tour algorithm. Note that here the measures are calculated on
non-binned data. The observed behaviour is smooth (much in contrast to
the behaviour of the scagnostics measures) and we next test the
behaviour in a guided tour, comparing again also the first and final
projection. (which index to select, will try both below\ldots{})

{\centering \includegraphics[width=\textwidth]{figure/mbgraphics-indices-1}

\caption[(ref:mbgraphics-indices)]{(ref:mbgraphics-indices)}\label{fig:mbgraphics-indices}
\end{figure}
\end{CodeChunk}

{\centering \includegraphics[width=\textwidth]{figure/guided-spline2d-plot-1} \includegraphics[width=\textwidth]{figure/guided-spline2d-plot-2} \includegraphics[width=\textwidth]{figure/guided-spline2d-plot-3}

\caption[(ref:guided-spline2d-plot)]{(ref:guided-spline2d-plot)}\label{fig:guided-spline2d-plot}
\end{figure}
\end{CodeChunk}

maybe move timing to the end, add also these indices in the same plot
(instead of testing several samples, behaviour anyway similar)
